Validation failed EVT

### 2022-09-26 analysis/article-results.Rmd
Updates to table 1/nomogram

```{r table-one-contin}
# Gives you everything for tables 1 and 2 (warnings due to variables not in validation, ignore!)
table_one <- dat_combined %>%  
  select(-all_of(c("sidescored", "AngleCcaIca", "ICAEAtherosclerosis", "StudySubjectID"))) %>%
  # Here we dichotomise purely for the table, does not affect original data
  mutate(
    ICA_nr_90orLarger_geq1 = factor(ifelse(ICA_nr_90orLarger >= 1, 1, 0)),
    ICA_nr_90orLarger_geq2 = factor(ifelse(ICA_nr_90orLarger >= 2, 1, 0)),
    ICAE_NASCET_99 = factor(ifelse(ICAE_NASCET_Degree < 99, 0,1)),
    InnCca_90orLarger_geq1 = factor(ifelse(InnCca_nr_90orLarger >= 1, 1, 0)),
    InnCca_90orLarger_geq2 = factor(ifelse(InnCca_nr_90orLarger >= 2, 1, 0)),
    ICAI_stenosis50 = factor(ifelse(ICAIAtherosclerosis == "Yes, >=50% stenosis", 1, 0)),
    AngleAaInn_OR_AaCca_dich45 = factor(ifelse(AngleAaInn_OR_AaCca > 45, 0, 1))
  ) %>% 
  CreateTableOne(data = ., strata = "dataset")

@@

```{r miss-dat-summ}
# Visualise missings beforehand
naniar::gg_miss_var(dat_to_impute, facet = dataset, show_pct = TRUE)
naniar::gg_miss_upset(dat_develop, nsets = 10, )
naniar::gg_miss_upset(dat_valid, nsets = 10)
```

@@

# Overestimation of risks
calplot_MI(
  imps_long = imps_valid,
  model = validation_dev_lambdamin$model_fit,
  impdat_ind = ".imp",
  model_formula = model_formula,
  height_hist = 0.2,
  startpos_hist = -0.25,
  knots = 5,
  n_bins = 200,
  xlim = c(0, 0.85),
  ylim = c(-0.25, 1)
) +
  theme_minimal()
```

@@

calplot_MI(
  imps_long = imps_combined,
  model = validation_comb_lambdamin$model_fit,
  impdat_ind = ".imp",
  model_formula = model_formula,
  height_hist = 0.2,
  startpos_hist = -0.25,
  knots = 5,
  n_bins = 200,
  xlim = c(0, 0.55),
  ylim = c(-0.25, 0.8)
) +
  theme_minimal()
```

@@

# Set variable labels
Hmisc::label(dat_nomogram$M_age) <- "Age (decades)"
Hmisc::label(dat_nomogram$M_prev_ht) <- "Hypertension"
Hmisc::label(dat_nomogram$AorticVariant) <- "Aortic variant"
Hmisc::label(dat_nomogram$ArchElongation) <- "Arch Elongation"
Hmisc::label(dat_nomogram$AngleFollowingBifurcation) <- "Angle post-bifurcation"
Hmisc::label(dat_nomogram$InnCca_nr_90orLarger) <- "CCA angles >=90 degr."
Hmisc::label(dat_nomogram$ICAE_NASCET_Degree) <- "ICA stenosis"

@@

# Edit some labels
mod_lrm <- lrm(model_formula, data = dat_nomogram)
mod_lrm$coefficients <- setNames(unname(drop(mod_coefs_comb)), names(mod_lrm$coefficients))

par(mar = c(2,2,1,1))
nom <- nomogram(
  fit = mod_lrm, 
  fun = plogis, 
  maxscale = 10, 
  funlabel = "Predicted probability", 
  lp = FALSE, 
  fun.at = c(.01, .05, seq(.1, 1, by = .1))
)

@@

@@

# Predict max prob
newpat <- dat_nomogram[1, ]
newpat$ArchElongation <- "III"
newpat$AngleFollowingBifurcation <- "Yes, angle >=90 degrees"
newpat$InnCca_nr_90orLarger <- ">=1"
newpat$ICAE_NASCET_Degree <- ">=99"
newpat$M_age <- 8
newpat

predict(mod_lrm, type = "fitted", newdata = newpat)
```

>>>>

```{r table-one-contin}
# ?tar_mermaid()

# Gives you everything for tables 1 and 2 (warnings due to variables not in validation, ignore!)
table_one <- select(.data = tar_read(develop_n887_raw), c("StudySubjectID", "M_mrs_rev")) |> 
  bind_rows(select(.data = tar_read(valid_n1111_raw), c("StudySubjectID", "M_mrs_rev"))) |> 
  rename("M_mrs_rev_orig" = "M_mrs_rev") |> 
  left_join(dat_combined) %>%  
  select(-all_of(c("sidescored", "AngleCcaIca", "ICAEAtherosclerosis", "StudySubjectID", "M_mrs_rev"))) %>%
  # Here we dichotomise purely for the table, does not affect original data
  mutate(
    ICA_nr_90orLarger_geq1 = factor(ifelse(ICA_nr_90orLarger >= 1, 1, 0)),
    ICA_nr_90orLarger_geq2 = factor(ifelse(ICA_nr_90orLarger >= 2, 1, 0)),
    ICAE_NASCET_99 = factor(ifelse(ICAE_NASCET_Degree < 99, 0,1)),
    InnCca_90orLarger_geq1 = factor(ifelse(InnCca_nr_90orLarger >= 1, 1, 0)),
    InnCca_90orLarger_geq2 = factor(ifelse(InnCca_nr_90orLarger >= 2, 1, 0)),
    ICAI_stenosis50 = factor(ifelse(ICAIAtherosclerosis == "Yes, >=50% stenosis", 1, 0)),
    AngleAaInn_OR_AaCca_dich45 = factor(ifelse(AngleAaInn_OR_AaCca > 45, 0, 1)),
    Mc_pretici_short = fct_collapse(
      Mc_pretici_short, 
      "<1" = c("0"),
      ">=1" = c("1", "2A", "2B, 2C or 3")
    ),
    M_collaterals = fct_collapse(
      M_collaterals,
      "<50" = c("absent collaterals", "filling <50% of occluded area"),
      ">=50" = c(">50% but less <100%", "100% of occluded area")
    ),
    M_ASPECTS_BL = factor(
      ifelse(M_ASPECTS_BL > 7, 0, 1),
      levels = c(0, 1),
      labels = c("8-10", "<=7")
    ),
    M_CBS_BL = factor(
      ifelse(M_CBS_BL > 7, 0, 1),
      levels = c(0, 1),
      labels = c("8-10", "<=7")
    ),
    M_posttici_c = fct_collapse(
      M_posttici_c,
      "2B-3" = c("2B", "2C", "3"),
      "0-2A" = c("0", "1", "2A")
    ),
    M_mrs_rev_orig = factor(
      ifelse(M_mrs_rev_orig >= 4, 0, 1),
      levels = c(0, 1),
      labels = c("0-2", "3-6")
    )
  ) %>% 
  CreateTableOne(data = ., strata = "dataset")

@@

```{r miss-dat-summ}
# Visualise missings beforehand
naniar::gg_miss_var(dat_to_impute, facet = dataset, show_pct = TRUE)
#naniar::gg_miss_upset(dat_develop, nsets = 10, )
#naniar::gg_miss_upset(dat_valid, nsets = 10)

dat_to_impute |> 
  group_by(dataset) |> 
  naniar::miss_var_summary() |> 
  mutate(across(where(is.numeric), ~ round(.x, 2L))) |> 
  DT::datatable(
    extensions = 'Buttons',
    options = list(
      dom = 'Blfrtip', 
      buttons = c('csv', 'excel', 'pdf'),
      lengthMenu = list(c(10, 25, 50, -1), c(10, 25, 50, "All"))
    )
  )  
```

@@

# Overestimation of risks
calplot_ext <- calplot_MI(
  imps_long = imps_valid,
  model = validation_dev_lambdamin$model_fit,
  impdat_ind = ".imp",
  model_formula = model_formula,
  height_hist = 0.2,
  startpos_hist = -0.25,
  knots = 5,
  n_bins = 200,
  xlim = c(0, 0.7),
  ylim = c(-0.25, 1)
) +
  theme_minimal() + 
  labs(x = "Predicted probability", y = "Observed proportion")

calplot_ext

ggsave(
  calplot_ext,
  filename = "analysis/figures/calibration-plot-ext.png",
  width = 8,
  height = 5,
  units = "in",
  dpi = 300, 
  bg = "white"
)
```

@@

calplot_combined <- calplot_MI(
  imps_long = imps_combined,
  model = validation_comb_lambdamin$model_fit,
  impdat_ind = ".imp",
  model_formula = model_formula,
  height_hist = 0.2,
  startpos_hist = -0.25,
  knots = 5,
  n_bins = 200,
  xlim = c(0, 0.55),
  ylim = c(-0.25, 0.8)
) +
  theme_minimal() +
  labs(x = "Predicted probability", y = "Observed proportion")

calplot_combined

ggsave(
  calplot_combined,
  filename = "analysis/figures/calibration-plot-combined.png",
  width = 8,
  height = 5,
  units = "in",
  dpi = 300, bg = "white"
)
```

@@

# Set variable labels
Hmisc::label(dat_nomogram$M_age) <- "Age (per decade)"
Hmisc::label(dat_nomogram$M_prev_ht) <- "Hypertension"
Hmisc::label(dat_nomogram$ArchElongation) <- "Aortic Arch Elongation"
Hmisc::label(dat_nomogram$AorticVariant) <- "Aortic variants"
Hmisc::label(dat_nomogram$InnCca_nr_90orLarger) <- "Tortuosity IA and CCA"
Hmisc::label(dat_nomogram$AngleFollowingBifurcation) <- "Tortuosity cervical ICA"
Hmisc::label(dat_nomogram$ICAE_NASCET_Degree) <- "ICA stenosis"

@@

# Edit some labels
model_formula_reorder <- Mc_FailedFemoralApproach ~ M_age + M_prev_ht + ArchElongation +
  AorticVariant + InnCca_nr_90orLarger + AngleFollowingBifurcation + ICAE_NASCET_Degree

# Annoying stuff to reorder
mod_lrm_reorder <- lrm(model_formula_reorder, data = dat_nomogram)
mod_lrm <- lrm(model_formula, data = dat_nomogram)
mod_lrm$coefficients <- setNames(unname(drop(mod_coefs_comb)), names(mod_lrm$coefficients))
mod_lrm_reorder$coefficients <- mod_lrm$coefficients[match(
  names(mod_lrm_reorder$coefficients), names(mod_lrm$coefficients)
)]

par(mar = c(2,2,1,1))
nom <- nomogram(
  fit = mod_lrm_reorder, 
  fun = plogis, 
  maxscale = 10, 
  funlabel = "Predicted probability", 
  lp = FALSE, 
  fun.at = c(.01, .05, seq(.1, 1, by = .1))
)

# Adjust levels
nom$`Tortuosity cervical ICA`$AngleFollowingBifurcation <- c("<90°", ">=90°") #°
nom$`Tortuosity IA and CCA`$InnCca_nr_90orLarger <- c("<90°", ">=90°") #°
nom$`ICA stenosis`$ICAE_NASCET_Degree <- c("<99%", ">=99%") #°
nom$`Aortic variants`$AorticVariant <- c("Normal", "Common origin\nIA-CCA", "Bovine arch") #°
nom$`Aortic Arch Elongation`$ArchElongation <- c("No elongation", "Mild to moderate", "Severe") #°

@@

# Printing points
print(nom, dec = 2L)

@@

# Predict max prob
newpat <- dat_nomogram[1, ]
newpat$ArchElongation <- "III"
newpat$AngleFollowingBifurcation <- "Yes, angle >=90 degrees"
newpat$InnCca_nr_90orLarger <- ">=1"
newpat$ICAE_NASCET_Degree <- ">=99"
newpat$M_age <- 10
newpat

predict(mod_lrm, type = "fitted", newdata = newpat)
dat_nomogram[which.max(predict(mod_lrm, type = "fitted", newdata = dat_nomogram)), ]
predict(mod_lrm, type = "fitted", newdata = dat_nomogram) |>  max()
```
